---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
<!-- output: rmarkdown::github_document -->
<!-- output: html_notebook -->



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# LUpak package

This is a repo for package that facilitates analysis for the agricultural conversion project.


To install the package run:
```{r install, eval = FALSE}
devtools::install_github("mirzacengic/LUpak")
```

*Made for personal use only!*

## Functions currenly added (without particular order):  
#### For modeling:  
- `variable_importance()` - calculate importance of predictor variables.  

- `get_rasters()` - load predictors for specific region.  

- `load_PA()`/`load_PA2()` - load response variable data (**needs to be fixed**)  

- `format_data()` - prepare data for modeling (return training and evaluation data). **There are some redundant VIF stuff still here.**  

- `vif_stepwise()`/`vif_select_vars()` - calculate VIF by stepwise elimination procedure.  

- `evaluate_model()`/`get_evaluations()` - Get model assessment results (AUC/TSS).  

- `fit_model()` - Fit linear model to the data.  

- `categorize_rasters()` - Create dummy variable rasters for categorical raster variables. Wraps around `raster::layerize()`. **Needs major overhaul!**

#### For data preparation:  
- `get_change_raster()` - Get differences between two rasters. **Optimized version!** Might have potential to be generalized for other people to use.  

- `get_change_raster_GDAL()` - alternative with GDAL and parallel implementation.  

- `rarify_points()` - Rarify points according to the raster grid. **Optimized version!**  

- `get_absences()` - Create absences for agricultural modeling.  


